---
title: "heatmap"
author: "Cheryl Logan"
date: "10/25/2019"
output: html_document
---

## Make a heatmap using heatmaply

Install necessary packages and load libraries. You only need to install the  packages once, but load libraries every time you open up a new R session.

```{r, eval = FALSE}
library(tidyverse) # after install.packages('tidyverse')
library(ggplot2)   # after install.packages('ggplot2')
library(heatmaply) # after install.packages('heatmaply')
```

Display working directory (equivalent of pwd in terminal) & change the working directory to location of your log transformed gene expression data file
```{r, eval = FALSE}
#getwd()
#setwd("/Users/path/to/your/library")
```

Load expression data (use log2 centered data)
```{r, }
fullgenelist <- read_csv("limma-voom_normalised_counts.csv")
# example data from DOI:10.5281/zenodo.2529926

fullgenelist <- select(fullgenelist,-ENTREZID,-GENENAME)

#subset full genelist to look for patterns
fullgenelist <- slice(fullgenelist,1:100) 
head(fullgenelist)
```

Make heatmap using heatmaply

```{r, }
#heatmaply(mtcars)
heatmaply(fullgenelist)
```
You can save an interactive version of your heatmaply into an HTML file using the following code:
```{r}
dir.create("folder")
library(heatmaply)
heatmaply(fullgenelist, file = "folder/heatmaply_plot.html")
browseURL("folder/heatmaply_plot.html")
```

Similar code can be used for saving a static file (png/jpeg/pdf)
```{r}
dir.create("folder")
library(heatmaply)
# Before the first time using this code you may need to first run:
# webshot::install_phantomjs()
heatmaply(fullgenelist, file = "folder/heatmaply_plot.png")
browseURL("folder/heatmaply_plot.png")
```
